04_DESeq_sexes

### 2019-08-28 analysis/04_DESeq2_sexes.Rmd
now with hyp, pit, gon

LDAanalysis <- function(mydds){
  # data prep
  vsd <- vst(mydds, blind=FALSE) # variance stabilized 
  tvsd <- as.data.frame(t(assay(vsd)))   # get vsd counts and transform

@@

  colDataPit <- subsetcolData2(c.colData, c("female_pituitary", "male_pituitary"))

  mydata <- left_join(tvsd, colDataPit, by = "V1")  # merge counts and variables

@@

LDAanalysis(dds.pituitary)
```

>>>>

LDAanalysis <- function(mydds, mycolData){
  # data prep
  vsd <- vst(mydds, blind=FALSE) # variance stabilized 
  tvsd <- as.data.frame(t(assay(vsd)))   # get vsd counts and transform

@@

  mydata <- left_join(tvsd, mycolData, by = "V1")  # merge counts and variables

@@

colDataHyp <- subsetcolData2(c.colData, c("female_hypothalamus", "male_hypothalamus"))
colDataPit <- subsetcolData2(c.colData, c("female_pituitary", "male_pituitary"))
colDataGon <- subsetcolData2(c.colData, c("female_gonad", "male_gonad"))

LDAanalysis(dds.hypothalamus, colDataHyp)
LDAanalysis(dds.pituitary, colDataPit)
LDAanalysis(dds.gonad, colDataGon)
```
